A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-10-01 journal/experiments.tex
missing word

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change may be
limited to changes in program state and data values.  However, the
vast majority of mutant repairs \emph{for a compiler} can be expected to also modify the code coverage of a
test; in our compiler experiments, there were no repairs that did not change
coverage; this would be very unlikely to hold in other software settings, where many bugs related to data values; for well-fuzzed compilers, however, few bugs are simple, e.g., off-by-one bugs in an integer value.  If a fault can be avoided by disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
coverage changed most often in repairs.  Early experiments with this
 approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

>>>>

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change may be
limited to changes in program state and data values.  However, the
vast majority of mutant repairs \emph{for a compiler} can be expected to also modify the code coverage of a
test; in our compiler experiments, there were no repairs that did not change
coverage; this would be very unlikely to hold in other software settings, where many bugs are related to data values; for well-fuzzed compilers, however, few bugs are simple, e.g., off-by-one bugs in an integer value.  If a fault can be avoided by disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
coverage changed most often in repairs.  Early experiments with this
 approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.
